%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj - modified by Alex Goldsmith
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://linkedin.com/alexander-goldsmith}{\Large Alex Goldsmith}} & 727 Lorillard CT Apt 105 Madison, WI 53703 \\
  \href{http://linkedin.com/alexander-goldsmith}{http://linkedin.com/alexander-goldsmith} & Email : \href{mailto:gold.alex.smith@gmail.com}{gold.alex.smith@gmail.com} \\
  \href{http://www.alexgoldsmith.me}{http://alexgoldsmith.me} & Mobile : +1-8644983481
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Epic}{Madison, WI}
      {Technical Solutions Engineer}{Dec. 2019 - Jun. 2021}
      \resumeItemListStart
        \resumeItem{Customer success}
          {Ensured continued success of 6 hospital system organizations live on Epic's registration and real-time eligibility applications through dozens of major software upgrades.}
        \resumeItem{Customer service quality}
          {Consistently maintained a success rate (greater than 90\%) for First Response Time targets within the top half of the application support team. }
        \resumeItem{Technical support}
          {Investigated techincal bugs encountered by customers via code walkthroughs, application testing, and code debugging. Provided customer-accepted resolution of 100\% of submitted issues.}
        \resumeItem{Project consulting}
          {Collaborated with customer IT teams to implement new features and develop specialized workflows.}
        \resumeItem{Incident escalation}
          {Owned high-impact customer issues from discovery to resolution, including issues within other Epic applications.}
        \resumeItem{Technical documentation} 
          {Documented customer requirements, technical bugs and broken workflows, application functionality, and user feedback.}
        \resumeItem{Mentorship and advising}
          {Provided technical expertise to a customer implementation project, while mentoring the customer's long-term support engineer.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Wisconsin-Madison}{Madison, WI}
      {Professional Capstone Certificate in Computer Sciences}{Dec. 2020 -- present}
    \resumeSubheading
      {Clemson University}{Clemson, SC}
      {Master of Arts in Economics}{Aug. 2018 -- Dec. 2019}
    \resumeSubSubheading
      {Bachelor of Arts in Economics}{Aug. 2015 -- May. 2018}
  \resumeSubHeadingListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Astro static site migration}
      {Currently working on a project to migrate legacy e-learning site to a modern design. I am using the Astro framework (JAMstack architecture) to design and build the new site.}
    \resumeSubItem{Badger Mental Health web and mobile application}
      {Participated in a team of 3 developers to create a web and mobile application with create/read/update/delete functionality for a course project. Stack included React front-end and NodeJs backend connecting to a document based database (Google Firebase).}
    \resumeSubItem{Stack Overflow Survey Visualization}
      {Created a web application for a course project using PyScript, JavaScript, and SQLite. The Web application allowed users to query a database, and subsequently displayed a visualization.}
  \resumeSubHeadingListEnd

%-----------Skills-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{C++, Java, MUMPS}
    \resumeSubItem{Scripting Languages}{Python, TypeScript, JavaScript}
    \resumeSubItem{Front-end Frameworks}{React, React-Native, Svelte, Astro}
    \resumeSubItem{Database Technologies}{SQL, SQLite, MySQL, SQL Server, MongoDB, Firebase, Relational \& Document Models}
    \resumeSubItem{Other Technologies}{NodeJS, Jest, Git, Docker, CMake, JSON, HTML, CSS, REST APIs, X12, LaTeX}
    \resumeSubItem{Cloud Platforms}{Google Cloud Platform (GCP), Microsoft Azure}
    \resumeSubItem{Other Languages}{Spanish: Limited working proficiency. ASL: Elementary proficiency.}
  \resumeSubHeadingListEnd

\section{Soft Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Leadership skills}{Competent and flexible team-leadership via carefully considered emotional intelligence.}
    \resumeSubItem{Organizational skills}{Capable time management through careful single-source of truth calendar use. Reliable task management with intelligent prioritiztion.}
    \resumeSubItem{Communication skills}{Skilled written (email, support tickets, technical documentation) and interpersonal communication.}
    \resumeSubItem{Creative skills}{Adept innovative and entreprenurial skills combined with problem-solving acumen.}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
