\documentclass[a4paper, 10pt]{letter}

% Name of sender
\name{Alex Goldsmith}

% Signature of sender
\signature{Alex Goldsmith}

% Address of sender
\address{Alex Goldsmith, \\
gold.alex.smith@gmail.com\\
}

\begin{document}
% Name and address of receiver
\begin{letter}
{
    Center for Healthy Minds,\\
    University of Wisconsin-Madison,\\
}
% Opening statement
\opening{Dear Center for Healthy Minds,}

% Letter body
I am writing to express my strong interest in the Research Software Developer position at the Center for Healthy Minds at the University of Wisconsin-Madison, as advertised. With a background in computer science and econometrics and a passion for using technology to support research and well-being, I am eager to contribute my skills and knowledge to further the mission of CHM.

My educational journey includes coursework in Computer Science at the University of Wisconsin - Madison, where I gained a solid foundation in programming languages such as C++, along with exposure to Linux systems. Additionally, my master's degree in Economics from Clemson University honed my analytical abilities and reinforced my commitment to research-driven endeavors.

During my tenure as a Technical Solutions Engineer at SpectrumAi and Epic Systems Corporation, I developed a proven track record of successfully managing technical issues, ensuring customer satisfaction, and providing innovative solutions. I have experience with a range of programming languages and have demonstrated the ability to adapt to dynamic requirements. Furthermore, my effective communication skills and teamwork make me well-suited to collaborate with scientists and researchers to achieve project goals.

What excites me most about the Research Software Developer role at CHM is the opportunity to blend my technical expertise with my passion for contributing to well-being research. As someone who values continuous learning and stays up-to-date with the latest advancements in technology, I am confident in my ability to create and support software and hardware solutions that facilitate research at CHM. I am enthusiastic about the prospect of building data collection platforms, coding behavioral tasks, and providing support for data collection hardware and software, all of which align with my skills and aspirations.

I am impressed by CHM's dedication to creating a welcoming and inclusive community, and I am excited about the prospect of contributing to such an environment. I am also committed to the pursuit of excellence in teaching, research, and outreach, and I believe that my background aligns perfectly with CHM's mission.

My resume provides further details about my education, work experience, and skills. I welcome the opportunity to discuss how my qualifications align with the needs of CHM in more detail.

Thank you for considering my application.

% Closing statement
\closing{Best regards,}

\end{letter}
\end{document}
