\documentclass[a4paper, 10pt]{letter}

% Name of sender
%\name{Alex Goldsmith}

% Signature of sender
\signature{Alex Goldsmith}

% Address of sender
%\address{Alex Goldsmith, \\
%gold.alex.smith@gmail.com\\
%}

	%-----------------------------------------------------------------------------%

	\begin{document}

	% Name and address of receiver
	\begin{letter}
	{
	   American Medical Association 
	}

		    % Opening statement
		    \opening{Dear AMA team,}

		    % Letter body

    I am applying to the position of Software Engineer I. I have robust experience executing the position's listed responsibilities via completed development projects at UW-Madison and my work experience at Epic Systems providing technical expertise, operational system support, and project support to health-care organization customers. 

    I am currently enrolled at University of Wisconsin-Madison working to earn a Capstone Certificate in Computer Sciences for Professionals. In Fall of 2021, I worked in an agile-based, three-person team to develop a mental-health cross-platform application. I contributed to both front-end (React-native) and back-end (NodeJS) development. I collaborated with team members to choose and implement a database solution (we ultimately chose a document-based model over a relational model). I also wrote all automated tests for the application using Jest. 

    From December 2020 to June 2021, I worked as a Technical Solutions Engineer at Epic Systems Corporation, where I supported six Healthcare Systems in the maintenance phase of the software development lifecycle, as well as one customer undergoing implementation. During that time, I worked remotely with IT teams all over the country to set priorities, troubleshoot issues, and discover creative solutions to various technical and business problems. My work with these customers included project support. For example, I provided instrumental technical expertise to a customer in a timely manner to aid a high-priority project implementing a High-Cost Drug cost reduction workflow. I additionally provided extensive operational system support to customers, aiding them in implementing and operationalizing new application features. My experience at Epic led me to pursue a more development focused career path, which is why I enrolled at UW-Madison.

		Prior to my tenure at Epic Systems Corporation, I graduated with a Masters of Economics from Clemson University. I used Python to process, analyze, and visualize data for my Master’s Thesis. Specifically, I wrote Python scripts to load data from a number of flat files, used the scikit-learn library to construct a number of analytical models, and created visualizations of the results using Matplotlib.

		I would be glad to speak further about how I may be an asset at the AMA. If you have any questions for me, please reach out over email at gold.alex.smith@gmail.com. 


		    % Closing statement
		    \closing{Best,}

		    \end{letter}
		    \end{document}
		    %-----------------------------------------------------------------------------%
