\documentclass[a4paper, 10pt]{letter}

% Name of sender
\name{Alex Goldsmith}

% Signature of sender
\signature{Alex Goldsmith}

% Address of sender
\address{Alex Goldsmith, \\
gold.alex.smith@gmail.com\\
}

	%-----------------------------------------------------------------------------%

	\begin{document}

	% Name and address of receiver
	\begin{letter}
	{
	    Cohere Health,\\
	}

		    % Opening statement
		    \opening{Dear Cohere Health team,}

		    % Letter body
			I am writing to express my strong interest in the Solutions Engineer role at Cohere Health. With deep expertise in software fundamentals and specific experience in healthcare technology, I believe I am an excellent fit for this opportunity.

			As demonstrated on my attached resume, I have a proven track record of partnering with clients to understand their unique needs, identify product gaps, and deliver customized solutions. In my most recent position at SpectrumAi, I served as the lead Solutions Engineer for our first major customer implementation. My technical expertise in React, Django, PostgreSQL, and systems integration enabled me to resolve issues and optimize the platform. I also developed scalable processes to support future implementations.

			In addition to my hands-on technical skills, I excel at communicating complex concepts clearly to both technical and non-technical stakeholders. My background in economics sharpened my ability to zoom out and understand the big picture, while still diving into details when needed. I am passionate about delivering an exceptional client experience and building strong relationships.

			I am inspired by Cohere Health's mission to eliminate friction in healthcare. My values align closely with your commitment to diverse, inclusive teams that make meaningful impacts. I would welcome the opportunity to join your solutions engineering team during this exciting growth phase. With my blend of technical knowledge, client focus, and team leadership, I am confident I could make immediate contributions.

			Thank you for your consideration. I look forward to discussing how I can help advance Cohere Health's goals. Please feel free to contact me if you would like any additional information.	
		    % Closing statement
		    \closing{Best,}
		    \end{letter}
		    \end{document}
		    %-----------------------------------------------------------------------------%
