\documentclass[a4paper, 10pt]{letter}

% Name of sender
\name{Alex Goldsmith}

% Signature of sender
\signature{Alex Goldsmith}

% Address of sender
\address{Alex Goldsmith, \\
gold.alex.smith@gmail.com\\
}

	%-----------------------------------------------------------------------------%

	\begin{document}

	% Name and address of receiver
	\begin{letter}
	{
	    Supply Chain Team,\\
	    Home Depot
	}

		    % Opening statement
		    \opening{Dear Supply Chain Team at Home Depot,}

		    % Letter body

		I am currently enrolled at University of Wisconsin-Madison working to earn a Capstone Certificate in Computer Sciences for Professionals. In Fall of 2021, I worked in a three-person team to develop a mental-health cross-platform application. I contributed to both front-end (Typescript) and back-end (NodeJS) development. I also wrote all automated tests for the application using Jest. 

		From December 2020 to June 2021, I worked as a Technical Solutions Engineer at Epic Systems Corporation, where I supported six Healthcare Systems in the maintenance phase of the software development lifecycle, as well as one customer undergoing implementation. During that time, I worked remotely with IT teams all over the country to set priorities, troubleshoot issues, and discover creative solutions to various technical and business problems. This experience led me to pursue a more development focused career path, which is why I enrolled at UW-Madison.

		Prior to my tenure at Epic Systems Corporation, I graduated with a Masters of Economics from Clemson University. I used Python to process, analyze, and visualize data for my Master’s Thesis. Specifically, I wrote Python scripts to load data from a number of flat files, used the scikit-learn library to construct a number of analytical models, and created visualizations of the results using Matplotlib.

		I would be glad to speak further about how I may be an asset at Home Depot. If you have any questions for me, feel free to reach out over email at gold.alex.smith@gmail.com or call me directly at 864-498-3481. 


		    % Closing statement
		    \closing{Best,}

		    \end{letter}
		    \end{document}
		    %-----------------------------------------------------------------------------%
